Untitled

### 2020-09-11 Rmd/brms_metric_selfing.Rmd
BRMS SELFING

This model contains both quantitative and qualitative data of selfing levels and the fixed effect is grouped in 4 categories of high, medium, low and none levels of selfing. The response variable is the integer of visits.

@@

c_e <- conditional_effects(m1.1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

@@

>>>>

This model uses both quantitative and qualitative data of selfing levels which is grouped in 4 categories: "high", "medium", "low" and "none". The response variable is the integer of visits. Note that the quantitative measurement that we use is autonomous fruit production and is grouped as follows: 0=none, >0-25=low, >25-75=medium; >75-100=high.

@@

c_e.1 <- conditional_effects(m1.1)
p1.1 <- plot(c_e.1, points=T,plot = FALSE)[[1]]

#ylim500
ggplot(data=p1.1[[1]], aes(x = autonomous_selfing_level, y = visits,color = ordered(autonomous_selfing_level))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1.1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=lower__, ymax=upper__), width=.1, color="black")+
  geom_point(data=p1.1[[1]], mapping=aes(x=autonomous_selfing_level, y=estimate__), color="black") + ylab("Visits") + xlab("Selfing level")+
  theme(legend.position = "none")

@@

c_e.1 <- conditional_effects(m1.1)
p1.1 <- plot(c_e.1, points=T,plot = FALSE)[[1]]

#ylim500
ggplot(data=p1.1[[1]], aes(x = autonomous_selfing_level, y = visits,color = ordered(autonomous_selfing_level))) +
  geom_point(data = all_df_2,alpha = 1/4) + 
  scale_fill_brewer(palette = "Greys") +
  scale_color_brewer(palette = "Set2") + theme_bw() +
  geom_errorbar(data=p1.1[[1]],mapping=aes(x=autonomous_selfing_level, ymin=lower__, ymax=upper__), width=.1, color="black")+
  geom_point(data=p1.1[[1]], mapping=aes(x=autonomous_selfing_level, y=estimate__), color="black") + ylab("Visits") + xlab("Selfing level")+
  theme(legend.position = "none") + ylim(0,500)
